### 2019-09-15 README.Rmd
readme cleanup

__Author:__ [Nima Hejazi](https://nimahejazi.org) and [Mark van der
  Laan](https://vanderlaan-lab.org)

@@

`methyvim` is an R package that provides facilities for differential methylation
analysis based on _variable importance measures_ (VIMs), a class of
statistically estimable target parameters that arise in causal inference.

The statistical methodology implemented computes targeted minimum loss-based
estimates of several well-characterized variable importance measures:

@@

For continous-valued treatments or exposures:

@@

_In all cases, an estimator of the target parameter is constructed via targeted
minimum loss-based estimation._

These methods allow differential methylation effects to be quantified in a
manner that is largely free of assumptions, especially of the variety exploited
in parametric models. __The statistical algorithm consists in several major
steps:__

@@

For a general discussion of the framework of targeted minimum loss-based
estimation, the many applications of this methodology, and the role the
framework plays in statistical causal inference, the recommended references are
@vdl2011targeted and @vdl2018targeted. @hernan2018causal and @pearl2000causality
may be of interest to those desiring a more general introduction to statistical
causal inference.

>>>>

__Authors:__ [Nima Hejazi](https://nimahejazi.org) and [Mark van der
  Laan](https://vanderlaan-lab.org)

@@

`methyvim` is an R package that provides facilities for differential methylation
analysis based on _variable importance measures_ (VIMs), statistical target
parameters inspired by causal inference.

The statistical methodology implemented computes targeted minimum loss estimates
of several well-characterized variable importance measures:

@@

For continuous-valued treatments or exposures (_WIP: support planned_):

@@

These methods allow differential methylation effects to be quantified in a
manner that is largely assumption-free, especially of the variety exploited
in parametric models. __The statistical algorithm consists in several major
steps:__

@@

For a general discussion of the framework of targeted minimum loss estimation
and its myriad applications, the canonical references are @vdl2011targeted and
@vdl2018targeted. @hernan2018causal and @pearl2000causality may be of interest
to those desiring a more general introduction to statistical causal inference.
